\textsc{LiveRec}: Framing Debug Protocols to Hotwire Probes

### 2023-08-10 paper/paper.tex
clear installation

\begin{table}[!ht]
  %\centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabular}{lrlrl}
      \toprule
      Implementation & \multicolumn{2}{l}{\#SLOC Probe Server} & \multicolumn{2}{l}{\#SLOC Keep-Alive Agent} \\
      \midrule
      Java JDI & 521 & Java & 77 & Java \\ 
      DAP Base & 267  & Python & --- & \\ 
      DAP Python & 142 & Python & 26 & Python \\ 
      DAP Java & 352 & Python & 115 & Java \\ 
      DAP Javascript & 257 & Python & 24 & Javascript \\ 
      DAP C & 188 & Python & 14 & C \\
      \bottomrule
  \end{tabular}
  \caption{Size of the language specific components in SLOC and their implementation languages.}
  \label{tab:sloc}
\end{table}

The table \ref{tab:sloc} shows the number of lines of code for the server part and the KAA for each implementation, with the language in brackets. The DAP Base line corresponds to the common code used by the other DAP-based implementations.
The tests were carried out with OpenJDK 20.0.2 for Java, Python 3.11.2 for Python and Node 18.16.1 for Javascript. The C code was compiled using GCC 13.1.1. The machine used to carry out the evaluations has an AMD Ryzen 5 2500U CPU and 8Gb of RAM.

>>>>

\begin{table}[!ht]
  %\centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabular}{lrlrl}
      \toprule
      Implementation & \multicolumn{2}{l}{\#SLOC Probe Server} & \multicolumn{2}{l}{\#SLOC Keep-Alive Agent} \\
      \midrule
      Java JDI & 521 & Java & 75 & Java \\ 
      DAP Base & 270  & Python & --- & \\ 
      DAP Python & 142 & Python & 26 & Python \\ 
      DAP Java & 360 & Python & 114 & Java \\ 
      DAP Javascript & 256 & Python & 24 & Javascript \\ 
      DAP C & 181 & Python & 14 & C \\
      \bottomrule
  \end{tabular}
  \caption{Size of the language specific components in SLOC and their implementation languages.}
  \label{tab:sloc}
\end{table}

The table \ref{tab:sloc} shows the number of lines of code for the server part and the KAA for each implementation, with the language in brackets. The DAP Base line corresponds to the common code used by the other DAP-based implementations.
The tests were carried out with OpenJDK 20.0.2 for Java, Python 3.11.2 for Python and Node 18.16.1 for Javascript. The C code was compiled using GCC 13.1.1 and GDB 13.2 was used for stack recording. The machine used to carry out the evaluations has an AMD Ryzen 5 2500U CPU and 8Gb of RAM.
